Measurement of the positive kaon-argon total hadronic differential cross section in the LArIAT experiment

### 2018-02-04 Chapter-0/0-Introduction.tex
s

The Standard Model is a gauge theory based on the local group of symmetry
\begin{equation}
G_{SM} = SU(3)_C  \otimes SU(2)_T \otimes U(1)_Y
\end{equation}

@@

\section{Neutrinos in the Standard Model}
The neutrino was introduced in the SM as a left-handed massless Weyl spinor.
The Dirac equation of motion
\begin{equation}
(i\gamma^ \mu \partial_\mu - m) \psi = 0
\end{equation}
for a fermionic field 
\begin{equation}
 \psi =  \psi_L +  \psi_R
\end{equation}
is equivalent to the equaitons
\begin{equation}
i\gamma^ \mu \partial_\mu  \psi_L = m \psi_R
\end{equation}
\begin{equation}
i\gamma^ \mu \partial_\mu  \psi_R = m \psi_L
\end{equation}

@@

\section{Beyond the Standard Model}
The discovery of neutrino oscillation and its implication of non-zero neutrino mass marks  the beginning of a new, exciting era in neutrino physics: the era of physics Beyond the Standard Model (BSM) in the neutrino sector.
We are currently searching for new, deeper theories that can accommodate neutrinos with non-zero mass, while remaining consistent with the rest of the Standard Model. %More excitingly, we need to probe these theories experimentally. 
\subsection{Neutrino Oscillations}
\subsection{Proton Decay}

>>>>

The Standard Model is a gauge theory based on the local group of symmetry
\begin{equation}
G_{SM} = SU(3)_C  \otimes SU(2)_T \otimes U(1)_Y
\label{eq:SMGroup}
\end{equation}

@@

\section{Neutrinos: in and beyond the Standard Model}
\subsection{Neutrino in the SM}
Neutrino were introduced in the SM as left-handed massless Weyl spinors.
The Dirac equation of motion
\begin{equation}
(i\gamma^ \mu \partial_\mu - m) \psi = 0
\end{equation}
for a fermionic field 
\begin{equation}
 \psi =  \psi_L +  \psi_R
\end{equation}
is equivalent to the equaitons
\begin{equation}
i\gamma^ \mu \partial_\mu  \psi_L = m \psi_R
\end{equation}
\begin{equation}
i\gamma^ \mu \partial_\mu  \psi_R = m \psi_L
\end{equation}

@@

\subsection{Neutrino Oscillations}
The determination of the flavor of a neutrino dynamically arises from the corresponding charged lepton associated in a CC interaction; for example, a $\nu_e$ is a neutrino which produces an $e^-$, a $\bar\nu_\mu$ is a neutrino which produces a $\mu^+$, $etc$. 
The neutrino flavor eigenstates $\ket{\nu_\alpha}$,  with $\alpha = e,\mu,\tau$, are orthogonal to each other and form a base for the the weak interaction matrix.

Overwhelming experimental data show neutrinos change flavor during their propagation. This phenomenon, predicted by Bruno Pontecorvo in 1957, is  called ``neutrino oscillations" and it is possible only if the flavor eigenstate are not identical to the mass eigenstates. A minimal extension of the Standard Model introduces three mass eigenstates, $\ket{\nu_i}$ ($i = 1,2, 3$), whose mass $m_i$ is well defined. 
The unitary Pontecorvo-Maki-Nakagawa-Sakata matrix transforms the spinor wave functions ($\psi$) of each component  between flavor and mass bases as follows

\begin{equation} 
\sum \psi_\alpha \ket{\nu_\alpha} =  \sum \psi_i \ket{\nu_i}, \rightarrow \psi_\alpha =  U_{PMNS} \psi_i, 
\end{equation}

with

\begin{equation}
U_{PMNS}=\\
\left[ 
\begin{array}{ccc}
c_{12} & s_{12} & 0\\
-s_{12} & c_{12} & 0\\
0 & 0 & 1\\
\end{array}
\right]
\left[ 
\begin{array}{ccc}
c_{13} & 0 &s_{13}e^{-i\delta} \\
0 & 1 & 0\\
-s_{13}e^{-i\delta}& 0 & c_{13}\\
\end{array}
\right]
\left[
\begin{array}{ccc}
1 & 0 & 0\\
0 & c_{23} & s_{23} \\
0& -s_{23} & c_{23} \\
\end{array}
\right]
\left[ 
\begin{array}{ccc}
e^{i\alpha_1} & 0 & 0\\
0& e^{i\alpha_2} & 0\\
0 & 0 & 1\\
\end{array}
\right]
\end{equation}

where $c$ e $s$ stand respectively for cosine and sine of the corresponding  mixing angles ($\theta_{12}$, $\theta_{23}$ and $\theta_{13}$), $\delta$ è is the Dirac CP violation phase, $\alpha_1$ and $\alpha_{2}$   è is the eventual Majorana CP violation phases.

\textcolor{red}{Experimental results summary}

\section{Beyond the Standard Model}
The discovery of neutrino oscillation and its implication of non-zero neutrino mass mark  the beginning of a new, exciting era in neutrino physics: the era of physics Beyond the Standard Model (BSM) in the neutrino sector.
We are currently searching for new, deeper theories that can accommodate neutrinos with non-zero mass, while remaining consistent with the rest of the Standard Model. %More excitingly, we need to probe these theories experimentally.

\subsubsection{Open Questions in Neutrino Physics}
On one hand, the last X decades of experiments in neutrino oscillations brought spectacular advancements in the understanding of the oscillations pattern, measuring the neutrino mixing angles and mass splitting with a precision of less than 10\%.  On the other, it opened the field for a series of questions needing experimental answers. 
Critical challenges in the next decade will entail an even deeper understanding of the neutrino mixing pattern, investigation of the neutrino mass origin, neutrino number and nature, and assessing CP violation in the lepton sector.

Following the recommendation of the latest Particle Physics Project Prioritization Panel  \cite{ParticlePhysicsProjectPrioritizationPanel(P5):2014pwa}, the US  is dedicating substantial resources to the development of a short- and long- baseline neutrino program to address many of these fundamental questions.  This program pivots on the Liquid Argon Time Projection Chamber (LArTPC) detector technology which will be described in \ref{ch:1}.

The main goals of these research programs include:
\begin{itemize}
\item[-] Assessment of the existence of right-handed sterile neutrinos. 
\item[-] Determination of the sign of $\Delta m^2_{13}$ (or $\Delta m^2_{23}$), i.e., the ``neutrino mass ordering".
\item[-] Determination of the octant, i.e.  whether $\theta_{23}$ is maximal.
\item[-] Determination the status of CP symmetry in the lepton sector.
\end{itemize}

\textcolor{red}{Smallness of neutrino masses, link to GUTs}

\subsubsection{Towards a more fundamental theory}
Despite its highly predictive power, a number of conceptual issues arise in the SM which disfavor it to be a good candidate for a fundamental theory.

The SM rather complex group structure, where a gauge group is formed with the direct product of other three groups as shown in eq. \ref{eq:SMGroup},  is unexplained. Also, the SM fails to include a suitable dark matter candidate and a mechanisms that accounts for the baryon asymmetry of the universe. Within the SM, a total of 25 parameters remain seemingly arbitrary and need to be fitted to data: 3 gauge couplings, 9 charged fermion masses, 3 mixing angles and one CP phase in the CKM matrix, the Higgs mass and quartic coupling, $\theta_{QCD}$, 3 neutrino masses, 3 neutrino mixing angles, 1 Dirac phase and, eventually,  2 Majorana phases.

### 2018-02-04 Chapters/1-LArTPCs.tex
s

\chapter{Liquid Argon Detectors at the Intensity Frontier}
Following the recommendation of the latest Particle Physics Project Prioritization Panel  \cite{ParticlePhysicsProjectPrioritizationPanel(P5):2014pwa}, the US is dedicating substantial resources to the development of a short- and long- baseline neutrino program to address the fundamental questions in neutrino physics today. A large portion of this program pivots on the Liquid Argon Time Projection Chamber (LArTPC) detector technology. In the next few years, LArTPC experiments -- such as the Short-Baseline Neutrino program (SBN) and DUNE -- will be major players in the intensity frontier field.

>>>>

\chapter{Liquid Argon Detectors at the Intensity Frontier}\label{ch:1}
Following the recommendation of the latest Particle Physics Project Prioritization Panel  \cite{ParticlePhysicsProjectPrioritizationPanel(P5):2014pwa}, the US is dedicating substantial resources to the development of a short- and long- baseline neutrino program to address the fundamental questions in neutrino physics today. A large portion of this program pivots on the Liquid Argon Time Projection Chamber (LArTPC) detector technology. In the next few years, LArTPC experiments -- such as the Short-Baseline Neutrino program (SBN) and DUNE -- will be major players in the intensity frontier field.

### 2018-02-04 Chapters/6-TrackingOptimization.tex
s

\chapter{Tracking Optimization}
Your first chapter is probably an introduction. But who knows.

>>>>

\chapter{Tracking Optimization}
Understanding how kaons and pions are tracked inside the TPC and optimizing the reconstruction algorithms to maximize the correct identification of the interaction point is a fundamental step of the analysis.

\section{MC sample and WC2TPC match}
The optimization is performed on a MC sample of \textcolor{red}{HOW MANY?} kaons and \textcolor{red}{HOW MANY?} pions produced with the DDMC technique. 
DDMC particles are shot from the WC4 location into the TPC following the beam profile.
We mimic the matching between the WC and the TPC track on Monte Carlo by constructing a fake WC track using truth information at the true initial point. We then apply the same WC to TPC matching algorithm as in data.

Plots I want in this section:
\begin{enumerate}
\item WC2TPC MC DeltaX, DeltaY and $\alpha$
\item Delta L, reco - true
\item Delta L, reco - true Elastic, Delta L, reco - true Inelastic, other
\item Length Quality cut
\item Efficiency as a function of true KE and Angle
\end{enumerate}
